Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Implies That Modelling This Situation Using Other Models Would Be Better

### 2024-12-14 paper/paper.qmd
Fix one more final mistake in the qmd file of the paper, related to downloading the relevant packages
Rerender the pdf version of the paper

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#| 
# Download the packages if necessary. If packages are already 
# downloaded, comment out the following lines.
install.packages("tidyverse")
install.packages("opendatatoronto")
install.packages("janitor")
install.packages("dplyr")
install.packages("readr")
install.packages("knitr")
install.packages("kableExtra")
install.packages("arrow")
install.packages("ggplot2")
install.packages("MASS")
install.packages("here")

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
